DRAFT Example Kitsap County Pedestrian Facilities Metrics/Evaluation Report

### 2022-10-06 Draft Ped Metrics Example.Rmd
make sure only nc roads

getWalkingPolygonInCounty <- function(locdf, idcol) {
  # finds the items in locdf that are in the target area
  # then finds the polygon around them
  # then limits that again to the area in the target (because the polygon may go into a city)
  fdf <- st_intersection(locdf, st_buffer(county_no_cities,0)) 
  mb_isochrone(fdf,
               time = 30, "walking", id_column=idcol)
  #fdf <- st_transform(fdf, 9003)
  #st_intersection(fdf, st_buffer(county_no_cities,0)) 
}
library(mapboxapi)
lib_30min <- mb_isochrone(libraries,
               time = 30, "walking", id_column="NAME")
```

>>>>

getWalkingPolygonInCounty <- function(locdf, idcol) {
  # finds the items in locdf that are in the target area
  # then finds the polygon around them
  # then limits that again to the area in the target (because the polygon may go into a city)
  fdf <- st_intersection(locdf, st_buffer(county_no_cities,0)) 
  mb_isochrone(fdf,
               time = 30, "walking", id_column=idcol)
  #fdf <- st_transform(fdf, 9003)
  #st_intersection(fdf, st_buffer(county_no_cities,0)) 
  # doesn't do the clip off of the last part
}
library(mapboxapi)
lib_30min <- mb_isochrone(libraries,
               time = 30, "walking", id_column="NAME")
```

### 2022-10-06 child_single_geo.Rmd
store scores of breakdowns and builds isochrones
make sure only nc roads

this_geo <- st_as_sf(loop_df) %>% filter(tomatch == "{{current_geo}}") 
this_roads <- st_intersection(road_df, st_buffer(this_geo,0))
this_sw_sh <- st_intersection(nc_sw_sh, st_buffer(this_geo,0))

@@

>>>>

this_geo <- st_as_sf(loop_df) %>% filter(tomatch == "{{current_geo}}") 
this_roads <- st_intersection(ncdf, st_buffer(this_geo,0))
this_sw_sh <- st_intersection(nc_sw_sh, st_buffer(this_geo,0))

@@

```{r}
# add the score to the score breakdowns
if (!exists(deparse(substitute(this_comb_total_score)))){
  this_comb_total_score <- 0
}
score_breakdowns$Score[score_breakdowns$Area == "{{current_geo}}"] <- this_comb_total_score
```
